\begin{center} \bf \sffamily \LARGE Prisoner's dilemma with stochastic payoffs\\[-1cm] \end{center}

### 2021-04-22 main.tex
draft written parts

Evolutionary game theory is a mathematical framework for modeling evolution in
biological, social and economical systems. %ToDo references
Compared to classical game theory where it is assumed that players are rational,
evolutionary game theory does not require individuals to be rational. Instead
individuals adapt their strategies based on exploration and mutation. In this
context, strategies spread based on fitness either because the individuals who
adopt them have more offspring (fitness-based processes), or they are imitated
more often (pairwise comparison processes)~\cite{Wu2015}. Fitness is not
constant but it depends on the composition of the population. Individuals
interact with members of the population according to pre-define games, and their
payoffs are then translated into fitness.

Evolutionary models often work with idealized assumptions when estimating
fitness. It is commonly assumed that fitness is given by the mean payoff an
individual achieved over the different types in the population following
multiple intercalations. Referred to as the \textit{expected payoffs}. Expected
payoffs imply that individuals have a perfect a memory, as they are able to
recall several of their interactions with each player in the population. However
most evolutionary models, with a few notable exceptions~\cite{Hauert1997,
Stewart2016}, focus on naive subjects who can only choose from a restricted set
of strategies~\cite{Nowak1992tit}, or who do not remember anything beyond the
outcome of the very last round~\cite{Baek2016} when modeling how individuals
make decisions in each round. This creates a curious inconsistency. Individuals
make decisions in each round whist having very limited memory, however, when
modeling how individuals update their strategies over time, individuals are
assumed to have perfect memory.

One of the most important applications of evolutionary game theory is the
evolution of cooperation. Though cooperation can been seen to be at odd, several
mechanisms can allow for cooperation to emerge. One of these mechanisms is
direct reciprocity. However, given these idealized assumptions it feels like our
understanding of reciprocity is thus still incomplete. In this work we will
explore how robust our understanding of cooperation is as models deviate from
the perfect memory assumption.

This work is not the first to relax assumption made at the fitness level.
In~\cite{Roca2006} relax the assumption that selection occurs much more slowly
than the interaction between individuals. They results shows that rapid
selection affects evolutionary dynamics in such a dramatic way that for some
games it even changes the stability of equilibria.

We start by considering two extreme scenarios. The first is the classical
scenario of the expected payoffs and the alternative scenario where individuals
update their strategies only based on the very last payoff they obtained. We
refer to these as the \textit{stochastic} payoffs of individuals. In
Section~\ref{section:donation}, we explore the effect of the payoffs in the
cooperation rate given the donation game. We explore the difference between the
ratios as well as the effect of different model parameters. In
Section~\ref{section:2_by_2_games} we explore the cooperation rate for all the
important case of symmetric \(2 \times 2\) games. For the later part of the
section we also allow individuals to use more memory.

@@

\section{Model Setup}

@@

1. In the game stage, each player is randomly matched with some other player in
the population to interact in a number of instances of the game
\(\begin{pmatrix} R & S  \\ T & P \end{pmatrix}\). The number of interactions is
not fixed, on the contrast we consider that another interaction has a
probability $\delta$ to continue following each turn. We assume herein that
individuals at most make use of simple \textit{reactive strategies} make
decisions in each round. Reactive strategy are a set of memory-one strategies
that only take into account the previous action of the opponent. Reactive
strategies can be written explicitly as a vector \(\in \R_{3}\). More
specifically a reactive strategy \(s\) is given by \(s=(y, p, q)\) where \(y\)
is the probability that the strategy opens with a cooperation and \(p, q\) are
the probabilities that the strategy cooperates given that the opponent
cooperated and defected equivalently.

2. In the updating stage, two players are randomly drawn from the population, a
`learner' and a `role model'. Given that the learner's payoff $u_L\!\in\!
\mathcal{U}$ and that the role model's payoff $u_{RL}\!\in\! \mathcal{U}$, we
assume the learner adopts the role model's strategy with probability

\begin{equation} \label{Eq:rho}
\rho(u_L, u_{RL}) = \frac{1}{1\!+\!\exp\big[ \!-\!\beta (u_E\!-\!u_{RL}) \big]}.
\end{equation}

where $\beta\!\ge\!0$ corresponds  to relative influence of the payoffs on the
adopt the strategy of the other is controlled by an external parameter, the so
called intensity of selection.

We iterate this basic evolutionary step until either the mutant strategy goes
extinct, or until it fixes in the population (in which case the mutant strategy
becomes the new resident strategy). After either outcome, we introduce a new
mutant strategy $S'_2\!=\!(y_2',p_2',q_2')$ (uniformly chosen from all reactive
strategies at random), and we set the number of mutants to $k\!=\!1$. This
process of mutation and fixation/extinction is then iterated many times.xw The
fixation probability of the mutant strategy then takes the standard form
\cite{nowak2004emergence},

\begin{equation}
\varphi = \frac{1}{1+\sum_{i=1}^{N-1}\prod_k^i \frac{\lambda^-_k}{\lambda^+_k}}.
\end{equation}

where \(\lambda^-_k, \lambda^+_k\) are the probabilities that the number of
mutants decreases and increases respectively.

We compare this process for stochastic payoff evaluation with the analogous
process where players update their strategies with respect to their {\it
expected} payoffs,

\begin{equation} \label{Eq:ExpPay}
  \begin{array}{lcrcr}
  \displaystyle \pi_1	&=	&\displaystyle \frac{N\!-\!k\!-\!1}{N-1}\cdot \langle\mathbf{v}(S_1,S_1),\mathbf{u}\rangle	&+	&\displaystyle\frac{k}{N-1}\cdot \langle\mathbf{v}(S_1,S_2),\mathbf{u}\rangle,\\[0.5cm]
  \displaystyle \pi_2	&=	&\displaystyle\frac{N-k}{N-1}\cdot \langle\mathbf{v}(S_2,S_1),\mathbf{u}\rangle&+	&\displaystyle\frac{k-1}{N-1}\cdot \langle\mathbf{v}(S_2,S_2),\mathbf{u}\rangle.\\
  \end{array}
\end{equation}

% \subsection{Fixation probabilities under stochastic payoff evaluation}
% Given that $N\!-\!k$ players use the resident strategy $S_1\!=\!(y_1,p_1,q_1)$ and that the remaining $k$ players use the mutant strategy $S_2\!=\!(y_2,p_2,q_2)$, the probability that the number of mutants increases by one in one step of the evolutionary process can be written as
% \begin{equation}
% \lambda^+_k=\frac{N\!-\!k}{N}\cdot \frac{k}{N}\cdot \sum_{u_1,u_2\in\mathcal{U}} x(u_1,u_2)\cdot \rho(u_1,u_2).
% \end{equation}
% In this expression, $(N\!-\!k)/N$ is the probability that the randomly chosen learner is a resident, and $k/N$ is the probability that the role model is a mutant. The sum corresponds to the total probability that the learner adopts the role model's strategy over all possible payoffs $u_1$ and $u_2$ that the two player may have received in their respective last rounds. We use $x(u_1,u_2)$ to denote the probability that the randomly chosen resident obtained a payoff of $u_1$ in the last round of his respective game, and that the mutant obtained a payoff of $u_2$. Given that the payoffs are $u_1$ and $u_2$, the imitation probability is then given by $\rho(u_1,u_2)$, as specified by Eq.~(\ref{Eq:rho}). The probability that the respective payoffs of the players are given by $u_1$ and $u_2$ can be calculated as
% \begin{equation}
% \setlength{\arraycolsep}{1pt}
% \begin{array}{llrl}
% x(u_1,u_2)	 &=&\displaystyle \frac{1}{N\!-\!1}\cdot  &v_{u_1}(S_1,S_2)\cdot 1_{(u_1,u_2)\in \mathcal{U}^2_F}\\[0.5cm]
% &+	
% &\displaystyle \left(1\!-\!\frac{1}{N\!-\!1}\right)  
% &\left[ \frac{k\!-\!1}{N\!-\!2}\frac{k\!-\!2}{N\!-\!3} v_{u_1}(S_1,S_2) v_{u_2}(S_2,S_2) + 
%  \frac{k\!-\!1}{N\!-\!2}\frac{N\!-\!k\!-\!1}{N\!-\!3} v_{u_1}(S_1,S_2) v_{u_2}(S_2,S_1)\right.\\[0.5cm]
% &&&\left. +\frac{N\!-\!k\!-\!1}{N\!-\!2}\frac{k\!-\!1}{N\!-\!3} v_{u_1}(S_1,S_1) v_{u_2}(S_2,S_2) + 
%  \frac{N\!-\!k\!-\!1}{N\!-\!2}\frac{N\!-\!k\!-\!2}{N\!-\!3} v_{u_1}(S_1,S_1) v_{u_2}(S_2,S_1)\right].
% \end{array}
% \end{equation}
%  The first term on the right side corresponds to the case that the learner and
%  the role model happened to be matched during the game stage, which happens
%  with probability $1/(N\!-\!1)$. In that case, we note that only those payoff
%  pairs can occur that are feasible in a direct interaction, $(u_1,u_2)\in
%  \mathcal{U}^2_F:=\big\{ (R,R), (S,T), (T,S), (P,P) \big\}$, as represented by
%  the respective indicator function. Otherwise, if the learner and the role
%  model did not interact directly, we need to distinguish four different cases,
%  depending on whether the learner was matched with a resident or a mutant, and
%  depending on whether the role model was matched with a resident or a mutant.

% \begin{equation}\label{eq:game}
%     \begin{pmatrix}
%         R & S  \\
%         T & P
%     \end{pmatrix}
% \end{equation}

% These cases include the Snowdrift~\cite{sugden2004economics} ($T>R>P>S$), Stag
% Hunt~\cite{skyrms2001stag} ($T>R>P>S$), Harmony~\cite{Licht1999} ($T>R>P>S$) and
% the Prisoner's Dilemma ($T>R>P>S$) games. The results based on these well know
% \(2 \times 2\) games are discussed in Section~\ref{section:2_by_2_games}.

@@

We first explore the effect of stochastic payoffs on the cooperative behaviour
by considering the extreme case that an individual's fitness is based on their
last interaction with one other individual. We compare this to the expected
payoffs. Figure~\ref{fig:expected_and_stochastic_for_donation} shows simulation
results for the described process of Section~\ref{section:methods}.

In Section~\ref{section:donation}, we will specifically consider the donation
game where each player can cooperate by providing a benefit \(b\) to the other
player at their cost \(c\), with \(0 < c < b\). Then, \(T=b, R=b-c, S=-c, P=0\),
and matrix~(\ref{eq:game}) is give by:

@@

Figure~\ref{fig:expected_and_stochastic_for_donation}~depicts the evolving
conditional cooperation probabilities $p$ and $q$ (assuming that the discount
factor~$\delta$ and the benefit $b$ are comparably high). The left panel
corresponds to the standard scenario considered in the previous literature. It
considers players who use expected payoffs to update their strategies. The right
panel shows the scenario considered herein, in which players update their
strategies based on their last round's payoff. The figure suggests that when
updating is based on expected payoffs, players tend to be more generous (their
$q$-values are higher on average). In addition, players are generally more
cooperative.

There is a statistically significant different in the cooperation distribution of
the population over time. The cooperation rate falls significantly yo under 50\%.
There results are true for a strong selection strength ($\beta=10$). The follow
up question that arises is what effect does the selection strength have on the
cooperation rate?

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=\textwidth]{static/expected_and_stochastic_for_donation_game_b_10.pdf}
    \caption{{\bf Evolutionary dynamics under expected payoffs and stochastic payoffs.} 
    We have run two simulations of the evolutionary process described in
    Section~\ref{section:methods} for $T\!=\!10^7$ time steps. For each time step,
    we have recorded the current resident population ($y,p,q$). Since simulations
    are run for a relatively high continuation probability of $\delta\!=\!0.999$, we
    do not report the players' initial cooperation probability $y$. The graphs show
    how often the resident population chooses each combination ($p,q$) of
    conditional cooperation probabilities in the subsequent rounds. ({\bf A}) If
    players update based on their expected payoffs, the resident population
    typically applies a strategy for which $p\!\approx\!1$ and
    $q\!\le\!1\!-\!c/b\!=\!0.9$. The cooperation rate within the resident population
    (averaged over all games and over all time steps) is close to 100\%. ({\bf B})
    When players update their strategies based on their realized payoffs in the last
    round, there are two different predominant behaviors. The resident population
    either consists of defectors (with $p\!\approx\!q\!\approx\!0$) or of
    conditional cooperators. In the latter case, the maximum level of $q$ consistent
    with stable cooperation is somewhat smaller compared to the expected-payoff
    setting, $q\!<\!0.5$. Also the resulting cooperation rate is smaller. On
    average, players cooperate roughly in half of all rounds. Parameters:
    $N\!=\!100$, $b\!=\!3$, $c\!=\!1$, $\beta\!=\!1$, $\delta\!=\!0.999$.}
    \label{fig:expected_and_stochastic_for_donation}
\end{figure}

Figure~\ref{fig:cooperation_rate_over_betas} illustrates the results for
different runs of the evolutionary process where $\beta\in\{10 ^ -2, 10 ^ - 1, 10
^ 0, 10 ^ 1, 10 ^ 2\}$. In the case where $\beta=10 ^ -2$ the process is almost
random, as the effect of the payoffs is very small. The cooperation rate for
this case and the case of $\beta=10 ^ -1$ between the stochastic and expected
payoffs are the same. However, it is clear that this does not apply given 
$\beta \geq 1$. The difference in the cooperation rate increases, in the case
where for the stochastic payoffs it can drop to 10\%.

@@

Figure~\ref{fig:cooperation_rate_over_betas} illustrates the results for
different runs of the evolutionary process where $\beta\in\{10 ^ -2, 10 ^ - 1, 10
^ 0, 10 ^ 1, 10 ^ 2\}$. In the case where $\beta=10 ^ -2$ the process is almost
random, as the effect of the payoffs is very small. The cooperation rate for
this case and the case of $\beta=10 ^ -1$ between the stochastic and expected
payoffs are the same. However, it is clear that this does not apply given 
$\beta \geq 1$. The difference in the cooperation rate increases, in the case
where for the stochastic payoffs it can drop to 10\%.

\begin{figure}[!htbp]
    \centering
    \begin{subfigure}{.65\textwidth}
      \centering
      \includegraphics[width=\textwidth]{static/expected_for_selection_strenght.pdf}
      \includegraphics[width=\textwidth]{static/stochastic_for_selection_strenght.pdf}
    \end{subfigure}%
    \begin{subfigure}{.35\textwidth}
      \centering
      \includegraphics[width=\textwidth]{static/cooperation_rate_over_betas.pdf}
    \end{subfigure}
\caption{{\bf The evolution of cooperation for different parameter values.} 
While the previous figures depict the evolutionary outcome for fixed parameter
values, here we vary the benefit of cooperation $b$ and the strength of
selection $\beta$. In all cases, stochastic payoff evaluation tends to reduce
the evolving cooperation rates. Unless explicitly varied, the parameters of the
simulation are $N\!=\!100$, $b\!=\!3$, $c\!=\!1$, $\beta\!=\!1$,
$\delta\!=\!0.99$. Simulations are run for $T\!=\!5\times 10^6$ time steps for
each parameter combination.}
\end{figure}

@@

\section{Model Setup}\label{section:methods}

>>>>

One of the most important applications of evolutionary game theory is the
evolution of cooperation. Why is it that some individuals choose to help others
(increasing their payoff) at the expense of decreasing one's own payoff? During
the past decade, the literature on mechanisms that allow for cooperation, even
though it's seen to be at odd has been fruitful. One such mechanism is
repetition; the so called direct reciprocity. Theoretical researchers have been
using evolutionary models to understand how direct reciprocity allows
cooperation to evolve and which strategies are important for sustaining
cooperation.

Evolutionary game theory does not require individuals to be rational, instead
they adapt strategies based on mutation and exploration. Strategies with
high fitness are more likely to spread, either because the individuals who
adopt them have more offspring (fitness-based processes), or they are imitated
more often (pairwise comparison processes)~\cite{Wu2015}. The fitness of strategies,
and subsequently of the individuals, is not constant. Instead it depends on the
composition of the population. Individuals interact with other members of the
population according to their strategies. Their yielded payoffs, according to
pre defined games, are translated into fitness.

It is commonly assumed that fitness assimilates to the \textit{expected payoff},
which the mean payoff an individual achieved over the different types in the
population after multiple intercalations. Expected payoffs imply that
individuals have a perfect a memory. In order to estimate expected payoffs
individuals must be able to recall several of their interactions with each
player in the population. However, when modeling how they make decisions in each
round they assumed to have very limited memory. To be precise, most work on this
models focuses on naive subjects who can only choose from a restricted set of
strategies~\cite{Nowak1992tit}, or who do not remember anything beyond the
outcome of the very last round~\cite{Baek2016}, with a few notable
exceptions~\cite{Hauert1997, Stewart2016}.

This creates a curious inconsistency, which raises the following question: how
robust is our understanding of cooperation? We are not the first to question the
assumptions of models when estimating fitness. In~\cite{Roca2006} relax the
assumption that selection occurs much more slowly than the interaction between
individuals. They results shows that rapid selection affects evolutionary
dynamics in such a dramatic way that for some games it even changes the
stability of equilibria.

We consider two cases. Initially, we start by considering two extreme scenarios.
The first is the classical scenario of the expected payoffs and the alternative
scenario where individuals update their strategies only based on the very last
payoff they obtained. We refer to these as the \textit{stochastic} payoffs of
individuals. We do this for the donation games but also the important cases of
symmetric \(2 \times 2\) games. These include the prisoner's dilemma, the
snowdrift game, the stag hunt game and the harmony game.

In the later sections we allow individuals to use more memory. More specifically,
individuals update their strategies by considering up to the last two rounds,
whilst interacting with up to two different players.

@@

\section{Model Setup}\label{section:model}

@@

In the game stage, each player is randomly matched with some other player in
the population to interact in a number of turns.  The number of turns is
not fixed, on the contrast we consider that another interaction has a
probability $\delta$ to continue following each turn. At each turn the players can
choose to either cooperate (C) or to defect (D). The payoffs in a given round
depend on both player's decisions and are given by:

\begin{equation*}\label{eq:game}
  U = \begin{pmatrix} R & S  \\ T & P \end{pmatrix}
\end{equation*}

We assume herein that
individuals at most make use of simple \textit{reactive strategies} make
decisions in each round. Reactive strategy are a set of memory-one strategies
that only take into account the previous action of the opponent. Reactive
strategies can be written explicitly as a vector \(\in \R_{3}\). More
specifically a reactive strategy \(s\) is given by \(s=(y, p, q)\) where \(y\)
is the probability that the strategy opens with a cooperation and \(p, q\) are
the probabilities that the strategy cooperates given that the opponent
cooperated and defected equivalently.

In the updating stage, two players are randomly drawn from the population, a
`learner' and a `role model'. Given that the learner's payoff $u_L\!\in\!
\mathcal{U}$ and that the role model's payoff $u_{RL}\!\in\! \mathcal{U}$, we
assume the learner adopts the role model's strategy based on the Fermi
distribution function. The relative influence of the payoffs on the
adopt the strategy of the other is controlled by an external parameter. The so
called intensity of selection,  $\beta\!\ge\!0$.

This basic evolutionary step is repeated until either the mutant strategy goes
extinct, or until it fixes in the population, in which case the mutant strategy
becomes the new resident strategy. After either outcome, we introduce a new
mutant strategy, uniformly chosen from all reactive strategies at random, and we
set the number of mutants to $k\!=\!1$. This process of mutation and
fixation/extinction is then iterated many times.

In this work we explore the effect on the payoffs in the updating stage. The
details of the process described in this section can be found in
appendix~\ref{appendix:methods}.

@@

We first explore the effect of stochastic payoffs on the cooperative behaviour
by considering the extreme case that an individual's fitness is based on their
last interaction with one other individual. We compare this to the expected
payoffs. In this section we consider the donation game.
Each player can cooperate by providing a benefit \(b\) to the other
player at their cost \(c\), with \(0 < c < b\). Then, \(T=b, R=b-c, S=-c, P=0\),
and matrix~(\ref{eq:game}) is give by:

@@

Figure~\ref{fig:expected_and_stochastic_for_donation} shows simulations results
for the described process of section~\ref{section:model}.
Figure~\ref{fig:expected_and_stochastic_for_donation}~depicts the evolving
conditional cooperation probabilities $p$ and $q$. Assuming that the discount
factor~$\delta$ is comparably high, the opening move \(y\) is a transient effect
and has not effect on the outcome.
The left panels corresponds to the standard scenario considered in the previous
literature. It considers players who use expected payoffs to update their
strategies. The right panel shows the scenario considered herein, in which
players update their strategies based on their last round's payoff. The top
panels assume a benefit of 3, whereas the bottom assume that the benefit is 10.

The figure suggests that when updating is based on expected payoffs, players
tend to be more generous. The $q$-values are higher on average which suggests
that individuals tend to cooperating more after they are at the receiving end
of a defection. In addition, for both cases of \(b\), individuals tend to
be more cooperative. The average cooperation rate is strictly higher for expected
payoffs. This difference is statistically important, abd the effect is even more
obvious when the benefit is higher. More specifically, for \(b=10\) the average
cooperation rate drops from 97\% to 51\%.

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=.75\textwidth]{static/expected_and_stochastic_for_donation_game.pdf}\vspace{-3cm}
    \includegraphics[width=.75\textwidth]{static/expected_and_stochastic_for_donation_game_b_10.pdf}
    \caption{{\bf Evolutionary dynamics under expected payoffs and stochastic payoffs.} 
    We have run two simulations of the evolutionary process described in
    Section~\ref{section:methods} for $T\!=\!10^7$ time steps. For each time step,
    we have recorded the current resident population ($y,p,q$). Since simulations
    are run for a relatively high continuation probability of $\delta\!=\!0.999$, we
    do not report the players' initial cooperation probability $y$. The graphs show
    how often the resident population chooses each combination ($p,q$) of
    conditional cooperation probabilities in the subsequent rounds. ({\bf A}) If
    players update based on their expected payoffs, the resident population
    typically applies a strategy for which $p\!\approx\!1$ and
    $q\!\le\!1\!-\!c/b\!=\!0.9$. The cooperation rate within the resident population
    (averaged over all games and over all time steps) is close to 100\%. ({\bf B})
    When players update their strategies based on their realized payoffs in the last
    round, there are two different predominant behaviors. The resident population
    either consists of defectors (with $p\!\approx\!q\!\approx\!0$) or of
    conditional cooperators. In the latter case, the maximum level of $q$ consistent
    with stable cooperation is somewhat smaller compared to the expected-payoff
    setting, $q\!<\!0.5$. Also the resulting cooperation rate is smaller. On
    average, players cooperate roughly in half of all rounds. Parameters:
    $N\!=\!100$, $b\!=\!3$, $c\!=\!1$, $\beta\!=\!1$, $\delta\!=\!0.999$.}
    \label{fig:expected_and_stochastic_for_donation}
\end{figure}

Figure~\ref{fig:cooperation_rate_over_benefit} further explores the effect of the
benefit on the cooperation rate. In all cases, the stochastic payoffs evolution
tends to reduce the evolving cooperation rate. For the stochastic payoffs,
benefit appears to not make a difference once \(b > 5\), and on average
the evolving cooperation rate is at 50\%. The effect of benefit on the expected
payoffs smooths out after \(b > 6\), and the expected payoffs estimating
the evolving rate to be at 90\%.

\begin{figure}[!htbp]
  \centering
  \begin{subfigure}{.65\textwidth}
    \centering
    \includegraphics[width=\textwidth]{static/expected_for_selection_strenght.pdf}
    \includegraphics[width=\textwidth]{static/stochastic_for_selection_strenght.pdf}
  \end{subfigure}%
  \begin{subfigure}{.35\textwidth}
    \centering
    \includegraphics[width=\textwidth]{static/cooperation_rate_over_betas.pdf}
  \end{subfigure}
\caption{{\bf The evolution of cooperation for different benefit values.} 
Here, we vary the benefit of cooperation $b$. In all cases, stochastic payoff
evaluation tends to reduce the evolving cooperation rates. Unless explicitly
varied, the parameters of the simulation are $N\!=\!100$, $b\!=\!3$, $c\!=\!1$,
$\beta\!=\!1$, $\delta\!=\!0.99$. Simulations are run for $T\!=\!5\times 10^6$
time steps for each parameter
combination.}\label{fig:cooperation_rate_over_benefit}
\end{figure}

Figure~\ref{fig:cooperation_rate_over_betas} illustrates the results for
different runs of the evolutionary process where we vary the strength of
selection. In the case of a very small \(\beta < \beta=10 ^ -1\) he process is
almost random, as the effect of the payoffs is very small. Once payoff begin to
matter the difference is once again evident, with the expected payoffs always
overestimating the evolved cooperation rate.

@@

@@

\section{Model Setup}\label{appendix:methods}
